Probability

### 2016-04-18 prob.tex
prob.tex \subsection{Plan} updated...

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}

@@

In the remainder of the paper, we examine each of these assumptions
and consider variations motivated by computation in a world with
limited resources. In particular, we will consider a variant of the
Hilbert space over finite fields; we will consider set-valued
probability measures; we will consider ways other than the Born rule
in which a state can induce a probability measure, and we will consider
probability measures that may come from information beyond the quantum
states.

>>>>

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\ffzd}[1]{{\mathbb{F}^{d\;*}_{#1}}}

@@

In the remainder of the paper, we examine each of these assumptions
and consider variations motivated by computation in a world with limited
resources. In particular, we will consider a variant of the Hilbert
space over finite fields~$\mathbb{F}_{p^{2}}^{d}$. Instead of $\left[0,1\right]$,
we will consider set-valued probability measures, in particular $\left\{ 0\right\} $,
impossible, and $\left(0,\infty\right)$, possible. Surprisingly,
some combinations of space and probability will result in no probability
measure or an unique probability measure. In these cases, there is
no need to discuss whether there is a Born rule, because we do not
have enough probability to correspond to every state.

If there may be more than one probability measure, we will discuss
whether there is a Born rule to generate a probability measure from
a state. When the space is $\mathbb{C}^{d}$, we will try to induced
a Born rule from the conventional Born rule; when the space is $\mathbb{F}_{p^{2}}^{d}$,
there is no natural way to induce a probability measure from a state,
so we will set some conditions a Born~$\tilde{\pi}$ should have:
\begin{itemize}
\item Given a pure state $\ket{\Psi}\in\ffzd{p^{2}}$, a Born-rule~$\tilde{\pi}$
should give a probability~$\tilde{\pi}_{\Psi}$;
\item $\ip{\Psi}{\Phi}=0\Leftrightarrow\tilde{\pi}_{\Psi}\left(\ket{\Phi}\right)=\tilde{0}$,
where $\tilde{0}$ is $0$ while considering $\left[0,1\right]$ and
$\tilde{0}$ is impossible while considering $\left\{ \textrm{impossible},\textrm{possible}\right\} $.
\item $\tilde{\pi}_{\Psi}\left(\ket{\Phi}\right)=\tilde{\pi}_{\mathbf{U}\ket{\Psi}}\left(\mathbf{U}\ket{\Phi}\right)\textrm{ ,}$where
$\ket{\Psi},\ket{\Phi}\in\ffzd{p^{2}}$ and $\mathbf{U}$ is any unitary
map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbbm{1}$. 
\end{itemize}
Notice that when the space is $\mathbb{C}^{d}$, every Born rule we
consider will satisfy these three conditions.

Finally, if there is a Born rule, we will see whether every probability
measure is induced by a state, and establish Gleason's theorem.
